---
title: "A Brief Introduction to Linear Models in R"
output:
  html_document:
      keep_md: TRUE
---

# Linear Models in R

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Many bioinformatics applications involving repeatedly fitting linear models to data.  Examples include:

* RNA-Seq differential expression analyses
* GWAS (for continuous traits)
* eQTL analyses
* Microarray data analyses
* and on and on ....

Understanding linear modelling in R is **critical** in implementing these types of analyses.

## Scope
* Basics of linear models
* R model syntax
* Understanding contrasts
* Models with continuous covariates

We will not discuss:

* Diagnostic plots 
* Data-driven model selection
* Anything that doesn't scale well when applied to 1000's of genes/SNPs/proteins

## Goals
A full course in linear models would take months, so this is a first introduction rather than a comprehensive how-to.  After this session you should:

* Have a general idea of what a linear model is
* Understand where linear models are used in bioinformatics
* Begin to understand model specification in R


<P style="page-break-before: always">


```{r, echo=FALSE}
htmltools::includeHTML("embed.html")
```


